What do incoming university students believe about open science practices in

### 2021-05-04 analysis/Manuscript.Rmd
some minor editing of references etc

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018). In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].  These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.

@@

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g. see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018]. In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.

@@

## The replication crisis
Interestingly, the vast majority of participants had not heard of "the replication crisis". Participants' estimates of the replicability of psychological studies was also near the midpoint of the possible range <!-- about 56% - need to code this in--> .

<!-- Something about what they thought the replication crisis was... There were a couple of open-ended follow-up items

Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies. However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
-->

@@

Overall these findings suggest that while incoming psychology students may have a degree of enthusiasm for open science norms, they know relatively little about replicability and open science.

@@

## Strengths and limitations

>>>>

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018]. In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].  These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.

@@

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g. see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].<!--I'm not sure what happened to these citations but I can't find them in our library anymore - need to fix --> In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.

@@

## The replication crisis
Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.

<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do think the replication is? Which scientific disciplines do you think are most affected by the replication crisis? We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to. -->

Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .

<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies. However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
-->

@@

Overall these findings suggest that while incoming psychology students may have a degree of sympathy for open science norms, they know relatively little about replicability and open science.

@@

## Strengths and limitations
Our study had a relatively large sample size, but used convenience/haphazard sampling. The results also reflect responses of just one sample of students at one point in time. Generalisations to a wider population of incoming students (or students beginning psychology students in the future) can be made only very tentatively. Our questions also focused primarily on attitudes and beliefs, rather than probing students' factual knowledge of findings or concepts.

<!--
More to say here.
-->
